What's in a name? On the (automated) topic naming of software maintenance activities

### 2010-03-01 icpc/icpc2010.tex
intro editting

>>>>

During the development of a software project developers touch on many issues integral to the purpose and specification of the software project. These issues are often referred to as topics. These topics can sometimes be automatically extracted from the changelog comments that developers create while committing revisions to the project's source control repository. Our previous work dealt with topic-trends, topics that repeat overtime. It seemed that these trends were often nonfunctional requirements.

Topics in this paper and the previous paper are word bags or word distributions. These word distributions are found via Latent Dirichlet Allocation~\cite{Blei2003}, which find independent word distributions shared among documents (changelog comments). The unfortunate aspect of topics that are word distributions is that they lack the tangibility of a rose. They do not self idea themselves due to their tangible properties. Topics have to be identified by interpretting the prevelant words in the word distribution and by inspecting related documents. This is tiresome when one has to handle more than one hundred different topics. It would be nice if we could glance at a topic and have some idea what it was about. This is the power of labelling and naming.

If a topic has a name or a label we immediately understand and register what it is. In our case the name is the bit of information that was missing from our topics to make them useful and complete.

In this paper we attempt to name or label development topics that were extracted from the history of a development project. In part
